Compositional Certified Resource Bounds

### 2015-04-15 paper/main.tex
spacing fix in table 2
move figure 3 just below figure 2
add the large figure as an appendix

\begin{table*}
\renewcommand{\max}[0]{{\rm mx}}
\nocaptionrule \caption{
  Comparison of the bounds generated by KoAT, Rank,
  LOOPUS, SPEED, and our tool $\toolname$ on several
  challenging linear examples. Results for KoAT and SPEED were extracted
  from previous publications because KoAT cannot take C programs as
  input in its current version and SPEED is not available.
  Entries marked with ? indicate that we cannot test the respective example with the tool. Entries
  marked with --- indicate that the tool failed to produce a result. We write
  $\max(a,b)$ for the maximum of $a$ and $b$.
}
\vspace{6pt}
\label{tab:eval}
\footnotesize

\newcommand{\dir}[2]{\texttt{#1} \\ \texttt{#2}}
\newcommand{\file}[2][c]{%
  \begin{tabular}[#1]{@{}r@{}}#2\end{tabular}}

File &
\multicolumn{2}{c|}{KoAT} &
\multicolumn{2}{c|}{Rank} &
\multicolumn{2}{c|}{LOOPUS} &
SPEED &
\toolname
\\

%--------------------------------------------
\hhline{=|==|==|==|=|=} \texttt{gcd.c} &

%--------------------------------------------
\hline \texttt{kmp.c} &

%--------------------------------------------
\hline \texttt{qsort.c} &

%--------------------------------------------
% \hline \file{\dir{speed\_pldi09}{fig1.c}} &
%
% ? &
% &
%
% --- &
% &
%
% $2 \max(n, 0)$ &
% $O(n)$ &
%
% God damn it &
%
% $1 + 2 |\inter 0 n|$
% \\

%--------------------------------------------
\hline \file{\dir{speed\_pldi09}{fig4\_2.c}} &

%--------------------------------------------
\hline \file{\dir{speed\_pldi09}{fig4\_4.c}} &

%--------------------------------------------
\hline \file{\dir{speed\_pldi09}{fig4\_5.c}} &

%--------------------------------------------
\hline \file{\dir{speed\_pldi10}{ex1.c}} &

%--------------------------------------------
\hline \file{\dir{speed\_pldi10}{ex3.c}} &

%--------------------------------------------
\hline \file{\dir{speed\_pldi10}{ex4.c}} &

%--------------------------------------------
\hline \file{\dir{speed\_popl10}{fig2\_1.c}} &

%--------------------------------------------
\hline \file{\dir{speed\_popl10}{fig2\_2.c}} &

%--------------------------------------------
\hline \file{\dir{speed\_popl10}{nstd\_multiple.c}} &

$\max(0, m{-}y) + \max(0, n{-}x)$ &

%--------------------------------------------
\hline \file{\dir{speed\_popl10}{nstd\_single.c}} &

%--------------------------------------------
\hline \file{\dir{speed\_popl10}{sqntl\_single.c}} &

%--------------------------------------------
\hline \file{\dir{speed\_popl10}{smpl\_multiple.c}} &

%--------------------------------------------
\hline \file{\dir{speed\_popl10}{smpl\_single2.c}} &

%--------------------------------------------
\hline \file{\dir{speed\_popl10}{smpl\_single.c}} &

%--------------------------------------------
\hline \file{\texttt{t07.c}} &

%--------------------------------------------
\hline \texttt{t08.c} &

%--------------------------------------------
\hline \texttt{t10.c} &

%--------------------------------------------
\hline \texttt{t11.c} &

%--------------------------------------------
\hline \texttt{t13.c} &

%--------------------------------------------
\hline \texttt{t15.c} &

%--------------------------------------------
\hline \texttt{t16.c} &

%--------------------------------------------
\hline \texttt{t19.c} &

%--------------------------------------------
\hline \texttt{t20.c} &

%--------------------------------------------
\hline \texttt{t27.c} &

%--------------------------------------------
\hline \texttt{t28.c} &

%--------------------------------------------
\hline \texttt{t30.c} &

%--------------------------------------------
\hline \texttt{t37.c} &

%--------------------------------------------
\hline \texttt{t39.c} &

%--------------------------------------------
\hline \texttt{t46.c} &

%--------------------------------------------
\hline \texttt{t47.c} &

@@

>>>>

@@

\begin{table*}[h!]
\appendix
\section{Complete Experimental Results for the Tool Comparison}

\renewcommand{\max}[0]{{\rm mx}}
\nocaptionrule \caption{
  Comparison of the bounds generated by KoAT, Rank,
  LOOPUS, SPEED, and our tool $\toolname$ on several
  challenging linear examples. Results for KoAT and SPEED were extracted
  from previous publications~\cite{GulwaniJK09,GulwaniMC09,GulwaniZ10,SinnZV14} because KoAT cannot take C programs as
  input in its current version and SPEED is not available.
  Entries marked with ? indicate that we cannot test the respective example with the tool. Entries
  marked with --- indicate that the tool failed to produce a result. We write
  $\max(a,b)$ for the maximum of $a$ and $b$.
}
\vspace{6pt}
\label{tab:eval}
\footnotesize

\newcommand{\dir}[2]{\code{#1} \\ \code{#2}}
\newcommand{\file}[2][c]{%
  \begin{tabular}[#1]{@{}r@{}}#2\end{tabular}}

Function &
\multicolumn{2}{c|}{KoAT} &
\multicolumn{2}{c|}{Rank} &
\multicolumn{2}{c|}{LOOPUS} &
SPEED &
\toolname
\\

%--------------------------------------------
\hhline{=|==|==|==|=|=} \code{gcd} &

%--------------------------------------------
\hline \code{kmp} &

%--------------------------------------------
\hline \code{qsort} &

%--------------------------------------------
% \hline \file{\dir{SPEED\ PLDI09}{fig1}} &
%
% ? &
% &
%
% --- &
% &
%
% $2 \max(n, 0)$ &
% $O(n)$ &
%
% God damn it &
%
% $1 + 2 |\inter 0 n|$
% \\

%--------------------------------------------
\hline \file{\dir{speed\ pldi09}{fig4\ 2}} &

%--------------------------------------------
\hline \file{\dir{speed\ pldi09}{fig4\ 4}} &

%--------------------------------------------
\hline \file{\dir{speed\ pldi09}{fig4\ 5}} &

%--------------------------------------------
\hline \file{\dir{speed\ pldi10}{ex1}} &

%--------------------------------------------
\hline \file{\dir{speed\ pldi10}{ex3}} &

%--------------------------------------------
\hline \file{\dir{speed\ pldi10}{ex4}} &

%--------------------------------------------
\hline \file{\dir{speed\ popl10}{fig2\ 1}} &

%--------------------------------------------
\hline \file{\dir{speed\ popl10}{fig2\ 2}} &

%--------------------------------------------
\hline \file{\dir{speed\ popl10}{nested\ multiple}} &

$\max(0, n{-}x) + \max(0, m{-}y) $ &

%--------------------------------------------
\hline \file{\dir{speed\ popl10}{nested\ single}} &

%--------------------------------------------
\hline \file{\dir{speed\ popl10}{sequential\ single}} &

%--------------------------------------------
\hline \file{\dir{speed\ popl10}{simple\ multiple}} &

%--------------------------------------------
\hline \file{\dir{speed\ popl10}{simple\ single2}} &

%--------------------------------------------
\hline \file{\dir{speed\ popl10}{simple\ single}} &

%--------------------------------------------
\hline \file{\code{t07}} &

%--------------------------------------------
\hline \code{t08} &

%--------------------------------------------
\hline \code{t10} &

%--------------------------------------------
\hline \code{t11} &

%--------------------------------------------
\hline \code{t13} &

%--------------------------------------------
\hline \code{t15} &

%--------------------------------------------
\hline \code{t16} &

%--------------------------------------------
\hline \code{t19} &

%--------------------------------------------
\hline \code{t20} &

%--------------------------------------------
\hline \code{t27} &

%--------------------------------------------
\hline \code{t28} &

%--------------------------------------------
\hline \code{t30} &

%--------------------------------------------
\hline \code{t37} &

%--------------------------------------------
\hline \code{t39} &

%--------------------------------------------
\hline \code{t46} &

%--------------------------------------------
\hline \code{t47} &
